\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/flexiblesusy-paper.tex
Add report numbers and acknowledgement
Intel Xeon has 2 CPUs with 6 cores each

\documentclass[final,3p,11pt,pdflatex]{elsarticle}
\usepackage[utf8x]{inputenc}      % input font encoding
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}          % output font encoding
\usepackage{booktabs,tabularx}
\usepackage{rotating}             % for sidewaystable
\usepackage{xspace}
\usepackage[usenames]{xcolor}
\usepackage{tikz,tikz-uml}
\usepackage{listings}
\bibstyle{elsarticle-num}
% source code highlighting
\lstset{breaklines=true,
  breakatwhitespace=true,
  stepnumber=1,
  basicstyle=\ttfamily\footnotesize,
  commentstyle=\ttfamily\color{gray},
  prebreak={\textbackslash},
  breakindent=10pt,
  breakautoindent=false,
  showspaces=false,
  showstringspaces=false,
  frame=single,
  abovecaptionskip=0em,
  aboveskip=1.5em,
  belowcaptionskip=0.5em,
  belowskip=1em,
}
\usepackage[pdftitle={FlexibleSUSY --- A spectrum generator generator for supersymmetric models},
pdfauthor={Peter Athron,Jae-hyeon Park,Dominik Stockinger,Alexander Voigt},
pdfkeywords={FlexibleSUSY,supersymmetry,spectrum,generator,MSSM,NMSSM,E6SSM},
bookmarks=true, linktocpage]{hyperref}

@@

@@

For the run-time comparison we're generating $2\cdot 10^{4}$ random
CMSSM parameter points with $m_0\in [50,1000]\unit{GeV}$, $m_{1/2}\in
[50,1000]\unit{GeV}$, $\tan\beta\in [1,100]$, $\sign\mu\in \{-1,+1\}$
and $A_0\in [-1000,1000]\unit{GeV}$.  For each point an SLHA input
file is created by appending the values of $m_0$, $m_{1/2}$,
$\tan\beta$, $\sign\mu$, $A_0$ in form of a \code{MINPAR} block to the
SLHA template file given in
\ref{sec:speed-test-slha-template-file}.  The resulting SLHA input
file is passed to each spectrum generator and the (wall-clock) time is
measured until the program has finished.  The average run-times for
three different CPU types can be found in
\tabref{tab:run-time-comparison}.  The first column shows the run-time
on a Intel Core2 Duo (P8600, $2.40\unit{GHz}$) where only one core was
enabled.  The second column shows the run-time on the same processor
where both cores were enabled.  In the third column a Intel Xeon
(L5640, $2.27\unit{GHz}$) was used, which has $6$ CPU cores.
%
\begin{table}[tbh]
  \centering
  \begin{tabular}{llll}
    \toprule
                            & Intel Core2 Duo    & Intel Core2 Duo   & Intel Xeon\\
                            & (P8600, 1 core)    & (P8600, 2 cores)  & (L5640, 6 cores)\\
    \midrule
    FlexibleSUSY-NoFV 1.0.0 & $0.086\unit{s}$    & $0.079\unit{s}$   & $0.060\unit{s}$\\
    SPheno 3.2.4            & $0.119\unit{s}$    & $0.114\unit{s}$   & $0.101\unit{s}$\\
    Softsusy 3.4.0          & $0.175\unit{s}$    & $0.171\unit{s}$   & $0.147\unit{s}$\\
    \midrule
    FlexibleSUSY-FV 1.0.0   & $0.150\unit{s}$    & $0.113\unit{s}$   & $0.074\unit{s}$\\
    SPhenoMSSM 4.1.0        & $0.415\unit{s}$    & $0.401\unit{s}$   & $0.370\unit{s}$\\
    \bottomrule
  \end{tabular}
  \caption{Average run-time of CMSSM spectrum generators
    for random parameter points.  The first three rows show
    spectrum generators which disallow flavour violation.  Rows
    $4$--$5$ contain flavour violating spectrum generators, based
    on SARAH's MSSM model file.}
  \label{tab:run-time-comparison}
\end{table}

@@

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models. The authors would also
like to thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Philip Diessner
for testing and identifying several bugs in \fs and in SARAH,
in work on the MRSSM; Ulrik Günther for compilation tests on Mac OS X
and Dylan Harries for spotting a bug in the configuration script.
%
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.

>>>>

\documentclass[final,3p,11pt,pdflatex]{elsarticle}
\usepackage[utf8x]{inputenc}      % input font encoding
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}          % output font encoding
\usepackage{booktabs,tabularx}
\usepackage{rotating}             % for sidewaystable
\usepackage{xspace}
\usepackage[usenames]{xcolor}
\usepackage{tikz,tikz-uml}
\usepackage{listings}
\usepackage[absolute]{textpos}
\bibstyle{elsarticle-num}
% source code highlighting
\lstset{breaklines=true,
  breakatwhitespace=true,
  stepnumber=1,
  basicstyle=\ttfamily\footnotesize,
  commentstyle=\ttfamily\color{gray},
  prebreak={\textbackslash},
  breakindent=10pt,
  breakautoindent=false,
  showspaces=false,
  showstringspaces=false,
  frame=single,
  abovecaptionskip=0em,
  aboveskip=1.5em,
  belowcaptionskip=0.5em,
  belowskip=1em,
}
\usepackage[pdftitle={FlexibleSUSY --- A spectrum generator generator for supersymmetric models},
pdfauthor={Peter Athron,Jae-hyeon Park,Dominik Stockinger,Alexander Voigt},
pdfkeywords={FlexibleSUSY,supersymmetry,spectrum,generator,MSSM,NMSSM,E6SSM},
bookmarks=true, linktocpage]{hyperref}

@@

% report numbers
\begin{textblock*}{7em}(\textwidth,1cm)
\noindent\footnotesize
FTUV--14--3904 \\
IFIC--14--40
\end{textblock*}

@@

For the run-time comparison we're generating $2\cdot 10^{4}$ random
CMSSM parameter points with $m_0\in [50,1000]\unit{GeV}$, $m_{1/2}\in
[50,1000]\unit{GeV}$, $\tan\beta\in [1,100]$, $\sign\mu\in \{-1,+1\}$
and $A_0\in [-1000,1000]\unit{GeV}$.  For each point an SLHA input
file is created by appending the values of $m_0$, $m_{1/2}$,
$\tan\beta$, $\sign\mu$, $A_0$ in form of a \code{MINPAR} block to the
SLHA template file given in
\ref{sec:speed-test-slha-template-file}.  The resulting SLHA input
file is passed to each spectrum generator and the (wall-clock) time is
measured until the program has finished.  The average run-times for
three different CPU types can be found in
\tabref{tab:run-time-comparison}.  The first column shows the run-time
on a Intel Core2 Duo (P8600, $2.40\unit{GHz}$) where only one core was
enabled.  The second column shows the run-time on the same processor
where both cores were enabled.  In the third column an Intel Xeon
(L5640, $2.27\unit{GHz}$) was used, which has two CPUs with $6$ cores
each.
%
\begin{table}[tbh]
  \centering
  \begin{tabular}{llll}
    \toprule
                            & Intel Core2 Duo    & Intel Core2 Duo   & Intel Xeon\\
                            & (P8600, $1$ core)  & (P8600, $2$ cores)& (L5640, $2\times 6$ cores)\\
    \midrule
    FlexibleSUSY-NoFV 1.0.0 & $0.086\unit{s}$    & $0.079\unit{s}$   & $0.060\unit{s}$\\
    SPheno 3.2.4            & $0.119\unit{s}$    & $0.114\unit{s}$   & $0.101\unit{s}$\\
    Softsusy 3.4.0          & $0.175\unit{s}$    & $0.171\unit{s}$   & $0.147\unit{s}$\\
    \midrule
    FlexibleSUSY-FV 1.0.0   & $0.150\unit{s}$    & $0.113\unit{s}$   & $0.074\unit{s}$\\
    SPhenoMSSM 4.1.0        & $0.415\unit{s}$    & $0.401\unit{s}$   & $0.370\unit{s}$\\
    \bottomrule
  \end{tabular}
  \caption{Average run-time of CMSSM spectrum generators
    for random parameter points.  The first three rows show
    spectrum generators which disallow flavour violation.  Rows
    $4$--$5$ contain flavour violating spectrum generators, based
    on SARAH's MSSM model file.}
  \label{tab:run-time-comparison}
\end{table}

@@

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models. The authors would also
like to thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Philip Diessner
for testing and identifying several bugs in \fs and in SARAH,
in work on the MRSSM; Ulrik Günther for compilation tests on Mac OS X
and Dylan Harries for spotting a bug in the configuration script.
%
J.P. acknowledges support from the MEC and FEDER (EC) Grants
FPA2011--23596 and the Generalitat Valenciana under grant PROMETEOII/2013/017.
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.
